---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# {skyphone}

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done
yet, or the repository is only intended to be a limited example, demo,
or
proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
[![R-CMD-check](https://github.com/matt-dray/skyphone/workflows/R-CMD-check/badge.svg)](https://github.com/matt-dray/skyphone/actions)
[![CodeFactor](https://www.codefactor.io/repository/github/matt-dray/skyphone/badge)](https://www.codefactor.io/repository/github/matt-dray/skyphone)
<!-- badges: end -->

The goal of {skyphone} is to create an audio version of a [GitHub Skyline](https://skyline.github.com/) in R.

Skyline is a novelty webservice from GitHub. You input a username and can 'view a 3D model of your GitHub contribution graph.' It looks a bit like a city skyline, hence the name. 

{skyphone} fetches the contributions data from the Skyline API and puts it in a nice, tidy table that you can sonify (i.e. convert to an audio signal) or plot.

Very much in development.

## Installation

You can install the {skyphone} package from GitHub:

```{r, install, eval=FALSE}
remotes::install_github("matt-dray/skyphone")
```

This assumes you've already installed {remotes} from CRAN with `install.packages("remotes")`

## Examples

The `sky_get()` function fetches from the Skyline API a named user's (open) contributions for a given year. Here's what it looks like to fetch my own contributions for 2020:

```{r example-fetch}
library(skyphone)
md <- sky_get("matt-dray", 2020)
md
```

You can hear contributions over time by passing the output from `sky_get()` to `sky_sonify()`. This function uses the {sonify} package to convert the data to audio format, where peaks are higher pitched.

```{r example-sonify}
sky_sonify(md, play = FALSE, out_dir = NULL)
```

You'll hear the output from your speakers if you set `play = TRUE` and/or save the audio file as a .wav to the folder provided by `out_dir`.

[`r emo::ji("speaker")` Click here to listen to the sonified output from this example.](https://www.rostrum.blog/output/skyphone/skyphone_matt-dray_2020.wav)

I've also included a simple, opinionated plotting function called `sky_plot`, which gives you a 2D representation of your 'skyline'.

```{r example-plot, fig.alt="A bar chart of contributions to GitHub in 2020 by user matt-dray, which peaks in the summer months."}
p <- sky_plot(md)
p
```

There's no reason why you couldn't mimic the vaporwave aesthetic of GitHub Skyline website using [the {vapoRwave} package](https://github.com/moldach/vapoRwave)...

```{r example-plot-vaporwave, fig.alt="A bar chart of contributions to GitHub in 2020 by user matt-dray, using a 'vaporwave' aesthetic for its colours and fonts."}
library(vapoRwave)  # install from GitHub
p + new_retro()
```

## Thanks

To GitHub, obviously. To [Matt Kerlogue](https://www.github.com/mattkerlogue) for the nerdsnipe. To Den Delimarsky for [writing about the Skyline API](https://den.dev/blog/get-github-contributions-api/).

## GitHub terms

You can read GitHub's [terms](https://docs.github.com/en/github/site-policy/github-terms-of-service) and [privacy statement](https://docs.github.com/en/github/site-policy/github-privacy-statement) for their service.

## Code of Conduct

Please note that the {skyphone} project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
