---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {skyphone}

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done
yet, or the repository is only intended to be a limited example, demo,
or
proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

The goal of {skyphone} is to create an audio version of [GitHub Skyline](https://skyline.github.com/) in R.

Skyline is a novelty vanity webservice from GitHub. You input a username and can 'view a 3D model of your GitHub contribution graph.' {skyphone} fetches this data and puts it in a nice, tidy table that you can sonify or plot.

Very much in development.

## Installation

You can install the development version of {skyphone} using {remotes}.

```{r, install, eval=FALSE}
# install.packages("remotes")
remotes::install_github("skyphone")
```

## Examples

I'll read in my own 2020 GitHub contributions from the Skyline API.

```{r example-fetch}
library(skyphone)
md <- sky_get("matt-dray", 2020)
md
```

You can make an audio version via the {sonify} package.

```{r example-sonify}
sky_sonify(md, play = FALSE, out_dir = NULL)
```

You can hear the output if you set `play = TRUE` and/or save the audio file as a .wav to the folder provided by `out_dir`. 

There's also a simple, opinionated built-in plotting function.

```{r example-plot}
sky_plot(md)
```

## Thanks

To GitHub, obviously. To [Matt Kerlogue](https://www.github.com/mattkerlogue) for the nerdsnipe. To Den Delimarsky for [writing about the Skyline API](https://den.dev/blog/get-github-contributions-api/).

## GitHub terms

You can read GitHub's [terms](https://docs.github.com/en/github/site-policy/github-terms-of-service), [privacy](https://docs.github.com/en/github/site-policy/github-privacy-statement) for their service.

## Code of Conduct

Please note that the skyphone project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
